---
title: "20180119WithinBird"
output: html_notebook
---



```{r}
library(tidyverse)
library(readxl)
library(glue)
```
  
  
#create a list of tibble
```{r}
dph <- excel_sheets("C:\\Users\\Oferlab_11\\Desktop\\New folder\\Subsong_now\\stability\\stabilityR658.xlsx")
WithinBird <- lapply(dph,
                      read_excel,
                      path = "C:\\Users\\Oferlab_11\\Desktop\\New folder\\Subsong_now\\stability\\stabilityR658.xlsx")
```



  

  
# Now tibblize list with bird names
```{r}
WithinBird <- tibble(day = dph, feature_distribution = WithinBird)
WithinBird
```

# annotating birdname to each observation using unnest
```{r}
WithinBirdfd <- WithinBird %>%
  unnest(feature_distribution)

WithinBirdfd
```


# turn it into long data
```{r}
WithinBirdeachfd_AMFM <- WithinBirdfd %>%
  gather(Time:Duration_of_state, key=feature, value=value) %>%
  group_by(feature, day) %>%
  filter(feature %in% c("AM","FM"))

WithinBirdeachfd_others <- WithinBirdfd %>%
  gather(Time:Duration_of_state, key=feature, value=value) %>%
  group_by(feature, day) %>%
  filter(!feature %in% c("AM","FM")) %>%
  filter(value != 0)
WithinBirdeachfd <- full_join(WithinBirdeachfd_AMFM,WithinBirdeachfd_others)

WithinBirdeachfd <- WithinBirdeachfd %>%
  summarize(value = list(value)) %>%
  spread(day, value) %>%
  group_by(feature)

WithinBirdeachfd
```
# remove 0
function(x) x <- x[ x != 0 ]

WithinBirdeachfd %>%
map(function(x) x <- x[ x != 0 ])


# YATTAZE2!
```{r}

colnameoftibble <- WithinBirdeachfd %>%
  colnames()

d1 = c(colnameoftibble[2:(length(dph)+1)])
d2 = c(colnameoftibble[2:(length(dph)+1)])
crossings <- crossing(d1,d2)


my_func <- function(d1, d2) {
  list( #do not use tibble here (that will make list name and pmap cannot handle later on)
  WithinBirdeachfd %>% slice(1) %>% pull(d1),
  WithinBirdeachfd %>% slice(1) %>% pull(d2)
  )
}

Asdf <- pmap(crossings, my_func)

my_func2 <- function(x, y) ks.test(x, y)

# perhaps this is good strategy, but does not work. need to convert . from list to double
KSstatresult <- Asdf %>% 
  modify_depth(1, ~ pmap(., my_func2)) %>%
  invisible() # suppress output
# here I want to also suppress warnings, but do not know how


combinedcolnames <- crossings %>% glue_data('{d1} vs {d2}')
#KSstatresult <- set_names(KSstatresult, combinedcolnames) %>%
#  invisible()

names(KSstatresult) <- combinedcolnames
KSstatresult_tibble <- as.tibble(KSstatresult)
KSstatresult_tibble <- KSstatresult_tibble %>%
  mutate(feature = unlist(WithinBirdeachfd$feature))
KSstatresult_tibble <- gather(KSstatresult_tibble, day, value, combinedcolnames)
KSstatresult_tibble <- KSstatresult_tibble %>%
  mutate(KSstatvalue = {
    map(.$value, "statistic")
    }
  )
KSstatresult_tibble <- KSstatresult_tibble %>%
  mutate(KSstatvalue = unlist(KSstatvalue))
KSstatresult_tibble2 <- KSstatresult_tibble %>%
  separate(day, c("d1","d2"), sep = ' vs ')
ghm <- ggplot(KSstatresult_tibble2, aes(x = d1, y = d2, fill = KSstatvalue))
ghm <- ghm + geom_tile()
ghm <- ghm + facet_wrap( ~ feature)
ghm <- ghm + scale_fill_gradient(limits=c(0,1))
ghm
```


```{r}
try <- KSstatresult_tibble %>% select(-value) %>% nest(-feature)
try[[2]] <- map(try[[2]], ~ separate(., day, c("d1","d2"), sep = ' vs '))
try[[2]] <- try[[2]] %>%
map(~filter(., d1 < d2)) #selecting only unique combi of d1-d2, works also for chr vectors
```


```{r}
WithinBirdeachfdaaa <- WithinBirdeachfd %>%
  gather(key=day, value=value,colnameoftibble[2:(length(dph)+1)]) %>%
  unnest(value)
WithinBirdeachfdaaa

```


# plot violins
```{r}
ggplot(WithinBirdeachfdaaa, aes(x = day, y = value), size = 1) +
  geom_violin(aes(fill = day), alpha = 0.5) +
  geom_boxplot(aes(fill = day), alpha = 0.8, width = 0.2) +
  facet_wrap(~ feature, scale = "free_x") +
  coord_flip()
```



